Approximation as Differentiation

### 2025-07-10 main/language.tex
Explain how interpretation of primitive types arrives in \Fam(\MeetSLat \times \JoinSLat^\op).

$\Fam(\MeetSLat \times \JoinSLat^\op)$ meets the requirements of $\Sem$: it is bicartesian closed
(\corref{mslat-jslat-bcc}), can model $\List(X)$ as an infinite coproduct
(\secref{models-of-total-gps:coproducts-and-products}), \roly{$\Lift$ monad, base types and operations.}

>>>>

Given an interpretation of base types and operations in $\Fam(\LatGal)$, the category $\Fam(\MeetSLat \times
\JoinSLat^\op)$ can implement $\Sem$. It is bicartesian closed (\corref{mslat-jslat-bcc}) and can model
$\List(X)$ as an infinite coproduct (\secref{models-of-total-gps:coproducts-and-products}). An interpretation
of base types and operations can be obtained from their interpretation in $\Fam(\LatGal)$ via the embedding
...
\roly{$\Lift$ monad.}
